FictionEro2 - Affective Impact of Fiction

### 2025-03-21 study2/analysis/1_cleaning.qmd
removed other + minor changes to scripts

```{r}
df <- filter(df, !Participant %in% outliers$arousal)
dftask <- filter(dftask, !Participant %in% outliers$arousal)
```

>>>>

Only `r sum(df$Gender=="Other")` participants self-reported as neither female nor male, hence they were excluded from further analysis.

```{r}
df<- filter(df, !Gender=="Other")
df <- filter(df, !Participant %in% outliers$arousal)
dftask <- filter(dftask, !Participant %in% outliers$arousal)
```

### 2025-03-21 study2/analysis/2_emotion.qmd
removed other + minor changes to scripts

```{r}
dfsub <- read.csv("../data/data_participants.csv")

@@

results_table <- function(model, effects="fixed", filter=NULL) {
  if("marginaleffects" %in% class(model)) {
    model |> 
      parameters::parameters() |> 
      as.data.frame() |> 
      select(-Parameter, -SE, -S, z=Statistic, -Predicted) |> 
      insight::format_table() |> 
      parameters::display()
  } else {
    display(parameters::parameters(model, effects=effects, keep=filter))
  }
}
```

@@

This section is about selecting the best model. Notably, all the stimuli presented are of an erotic nature.

@@

```{r}
arousal <- df |> 
  ggplot(aes(x=Arousal)) +
  geom_histogram(fill="grey", position = "identity", binwidth = 0.5) +
  scale_y_sqrt(expand = c(0, 0)) +
  scale_x_continuous(breaks = (0:6), labels = c("Not at all", "1", "2", "3", "4", "5", "Very much")) +
  labs(title = "Arousal") +
  theme_abyss() +
  theme(plot.title = element_text(hjust = 0.5, face="bold"))

@@

df |> 
  mutate(ConditionBelief = as.factor(ConditionBelief)) |> 
  mutate(ConditionBelief = case_when(
    ConditionBelief == "False" ~ "Not Believed",
    ConditionBelief == "True" ~ "Believed",)) |>
  ggplot(aes(x=Arousal, fill=Gender)) +
  geom_histogram(position = "identity", binwidth = 0.5) +
  facet_grid(Gender~ConditionBelief, scales="free_y") +
  scale_color_manual(values=c("red", "white"), guide="none") +
  scale_fill_manual(values=c("Female"="#E91E63", "Male"="#FF9800", "Other" = "#03A9F4"), guide="none") +
  # scale_y_sqrt(expand = c(0, 0)) +
  labs(title = "Arousal to images believed or not to be AI-Gnerated") +
  theme_abyss() +
  theme(plot.title = element_text(hjust = 0.5, face="bold"))
```

@@

test_bf(m1,m2)
compare_performance(m1, m2)

@@

This model evaluate ths the effects of Gender on Arousal, accounting for random variability due to participants (i.e., random effects). The analysis revealed that on average **women rate erotic stimuli significantly lower in arousal than men**, while participants identifying as 'other' rate on average erotic stimuli higher than men, however this is not significant.

```{r}
m_a <- glmmTMB::glmmTMB(Arousal ~ Gender + (1|Participant),
                      data=df, family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8))
                      # control = glmmTMB::glmmTMBControl(optimizer=stats::optim, # nlminb, optim
                      #                                   optArgs = list(method = "BFGS"),  #Nelder-Mead, BFGS, CG
                      #                                   parallel = 8))

@@

```{r}
estimate_relation(m_a) |> 
  ggplot(aes(x=Gender, y=Predicted)) +
  geom_pointrange(aes(ymin=CI_low, ymax=CI_high, color = Gender), position=position_dodge(width=0.5)) +
 scale_color_manual(values=c("Male"="#E91E63", "Female"="#FF9800","Other"="#03A9F4"), guide="none") +  labs(y="Arousal") +
  theme_abyss()
```

@@

```{r}
enticement <- df |> 
  ggplot(aes(x=Enticing)) +
  geom_histogram(fill="grey", position = "identity", binwidth = 0.5) +
  scale_y_sqrt(expand = c(0, 0)) +
  scale_x_continuous(breaks = (0:6), labels = c("Not at all", "1", "2", "3", "4", "5", "Very much")) +
  labs(title = "Enticement") +
  theme_abyss() +
  theme(plot.title = element_text(hjust = 0.5, face="bold"),
        legend.position = "none")

enticement
```

@@

df |> 
  mutate(ConditionBelief = as.factor(ConditionBelief)) |> 
  mutate(ConditionBelief = case_when(
    ConditionBelief == "False" ~ "Not Believed",
    ConditionBelief == "True" ~ "Believed",)) |>
  ggplot(aes(x=Enticing, fill=Gender)) +
  geom_histogram(position = "identity", binwidth = 0.5) +
  facet_grid(Gender~ConditionBelief, scales="free_y") +
  scale_color_manual(values=c("red", "white"), guide="none") +
  scale_fill_manual(values=c("Female"="#E91E63", "Male"="#FF9800", "Other" = "#03A9F4"), guide="none") +
  # scale_y_sqrt(expand = c(0, 0)) +
  labs(title = "Enticiment to images believed or not to be AI-Gnerated") +
  theme_abyss() +
  theme(plot.title = element_text(hjust = 0.5, face="bold"))
```

@@

The analysis revealed that on average **women rate erotic stimuli significantly lower in enticiment than men**, while participants identifying as 'other' rate on average erotic stimuli higher than men. However, these differences were not statistically significant.

```{r}
m_e <- glmmTMB::glmmTMB(Enticing ~ Gender + (1|Participant),
                      data=df,
                      control = glmmTMB::glmmTMBControl(parallel = 8))
                      # control = glmmTMB::glmmTMBControl(optimizer=stats::optim, # nlminb, optim
                      #                                   optArgs = list(method = "BFGS"),  #Nelder-Mead, BFGS, CG
                      #                                   parallel = 8))

@@

```{r}
estimate_relation(m_e) |> 
  ggplot(aes(x=Gender, y=Predicted)) +
  geom_pointrange(aes(ymin=CI_low, ymax=CI_high, color = Gender), position=position_dodge(width=0.5)) +
 scale_color_manual(values=c("Male"="#E91E63", "Female"="#FF9800","Other"="#03A9F4"), guide="none") +  labs(y="Arousal") +
  theme_abyss()
```

@@

```{r}
valence <- df |> 
  ggplot(aes(x=Valence)) +
  geom_histogram(fill="grey", position = "identity", binwidth = 0.5) +
  scale_y_sqrt(expand = c(0, 0)) +
  scale_x_continuous(breaks = (0:6), labels = c("Unpleasant", "1", "2", "3", "4", "5", "Pleasant")) +
  labs(title = "Valence") +
  theme_abyss() +
  theme(plot.title = element_text(hjust = 0.5, face="bold"),
        legend.position = "none")

@@

df |> 
  mutate(ConditionBelief = as.factor(ConditionBelief)) |> 
  mutate(ConditionBelief = case_when(
    ConditionBelief == "False" ~ "Not Believed",
    ConditionBelief == "True" ~ "Believed",)) |>
  ggplot(aes(x=Valence, fill=Gender)) +
  geom_histogram(position = "identity", binwidth = 0.5) +
  facet_grid(Gender~ConditionBelief, scales="free_y") +
  scale_color_manual(values=c("red", "white"), guide="none") +
  scale_fill_manual(values=c("Female"="#E91E63", "Male"="#FF9800", "Other" = "#03A9F4"), guide="none") +
  # scale_y_sqrt(expand = c(0, 0)) +
  labs(title = "Valence to images believed or not to be AI-Gnerated") +
  theme_abyss() +
  theme(plot.title = element_text(hjust = 0.5, face="bold"))
```

@@

The analysis revealed that on average **women rate erotic stimuli significantly lower in valence than men**, while participants identifying as 'other' rate on average erotic stimuli higher in valence than men but these was not statistically significant.

```{r}
m_v <- glmmTMB::glmmTMB(Valence ~ Gender + (1|Participant),
                      data=df,
                      control = glmmTMB::glmmTMBControl(parallel = 8))
                      # control = glmmTMB::glmmTMBControl(optimizer=stats::optim, # nlminb, optim
                      #                                   optArgs = list(method = "BFGS"),  #Nelder-Mead, BFGS, CG
                      #                                   parallel = 8))

@@

m_arousal <- glmmTMB::glmmTMB(Arousal ~ Gender/ Condition + 
                                (1| Participant) + (1|Stimulus), data=df, control = glmmTMB::glmmTMBControl(parallel = 8))

@@

# marginaleffects::avg_slopes(m_arousal, variables="Condition", by="Gender", re.form=NA) |> 
#   results_table()

@@

>>>>

```{r}
#| warning: false
#| 
dfsub <- read.csv("../data/data_participants.csv")

@@

results_table <- function(model, effects="fixed", filter=NULL) {
  if("marginaleffects" %in% class(model)) {
    model |> 
      parameters::parameters() |> 
      as.data.frame() |> 
      select(-Parameter, -SE, -S, z=Statistic, -Predicted) |> 
      insight::format_table() |> 
      parameters::display()
  } else {
    display(parameters::parameters(model, effects=effects, keep=filter))
  }
}

## re-scaled variables
scale_values <- function(x){(x-min(x))/(max(x)-min(x))}

df$Arousal <- scale_values(df$Arousal)
df$Enticing <- scale_values(df$Enticing)
df$Valence <- scale_values(df$Valence)
```

@@

This section is about selecting the best model. Notably, all the stimuli presented are of an erotic nature.
Note that variables were rescaled to [0,1] when fitting the models and that the stimuli presented to participants was assigned according to their self-rated sexuality, making all stimuli relevant to participants.

To summarise, women rate stimuli on average significantly lower in arousal, enticiment and valence than men.

@@

```{r}
arousal <- df |> 
  ggplot(aes(x=Arousal)) +
  geom_bar(fill="#03A9F4") +
  scale_y_sqrt(expand = c(0, 0)) +
  labs(title = "Arousal", ) +
  theme_abyss() +
  theme(plot.title = element_text(hjust = 0.5, face="bold"))

@@

df |> 
  mutate(ConditionBelief = as.factor(ConditionBelief)) |> 
  mutate(ConditionBelief = case_when(
    ConditionBelief == "False" ~ "Not Believed",
    ConditionBelief == "True" ~ "Believed",)) |>
  ggplot(aes(x=Arousal, fill=Gender)) +
  geom_bar(position = "identity") +
  facet_grid(Gender~ConditionBelief, scales="free_y") +
  scale_color_manual(values=c("red", "white"), guide="none") +
  scale_fill_manual(values=c("Female"="#E91E63", "Male"="#FF9800"), guide="none") +
  # scale_y_sqrt(expand = c(0, 0)) +
  labs(title = "Arousal to images believed or not to be AI-Gnerated") +
  theme_abyss() +
  theme(plot.title = element_text(hjust = 0.5, face="bold"))
```

@@

test_bf(m1,m2, m3)
compare_performance(m1, m2)

@@

This model evaluate ths the effects of Gender on Arousal, accounting for random variability due to participants (i.e., random effects). The analysis revealed that on average **women rate erotic stimuli significantly lower in arousal than men**.

m_a <- glmmTMB::glmmTMB(Arousal ~ Gender + (1|Participant),
                      data=df, family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8))
                      # control = glmmTMB::glmmTMBControl(optimizer=stats::optim, # nlminb, optim
                      #                                   optArgs = list(method = "BFGS"),  #Nelder-Mead, BFGS, CG
                      #                                   parallel = 8))

@@

```{r}
estimate_relation(m_a) |> 
  ggplot(aes(x=Gender, y=Predicted)) +
  geom_pointrange(aes(ymin=CI_low, ymax=CI_high, color = Gender), position=position_dodge(width=0.5)) +
 scale_color_manual(values=c("Male"="#E91E63", "Female"="#FF9800"), guide="none") +  labs(y="Arousal") +
  theme_abyss()
```

@@

```{r}
enticiment <- df |> 
  ggplot(aes(x=Enticing)) +
  geom_bar(fill="#03A9F4") +
  scale_y_sqrt(expand = c(0, 0)) +
  labs(title = "Enticement", ) +
  theme_abyss() +
  theme(plot.title = element_text(hjust = 0.5, face="bold"))

enticiment
```

@@

df |> 
  mutate(ConditionBelief = as.factor(ConditionBelief)) |> 
  mutate(ConditionBelief = case_when(
    ConditionBelief == "False" ~ "Not Believed",
    ConditionBelief == "True" ~ "Believed",)) |>
  ggplot(aes(x=Enticing, fill=Gender)) +
  geom_bar(position = "identity", binwidth = 0.5) +
  facet_grid(Gender~ConditionBelief, scales="free_y") +
  scale_color_manual(values=c("red", "white"), guide="none") +
  scale_fill_manual(values=c("Female"="#E91E63", "Male"="#FF9800"), guide="none") +
  # scale_y_sqrt(expand = c(0, 0)) +
  labs(title = "Enticiment to images believed or not to be AI-Gnerated") +
  theme_abyss() +
  theme(plot.title = element_text(hjust = 0.5, face="bold"))
```

@@

The analysis revealed that on average **women rate erotic stimuli significantly lower in enticiment than men**.

```{r}
m_e <- glmmTMB::glmmTMB(Enticing ~ Gender + (1|Participant),
                      data=df,family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8))
                      # control = glmmTMB::glmmTMBControl(optimizer=stats::optim, # nlminb, optim
                      #                                   optArgs = list(method = "BFGS"),  #Nelder-Mead, BFGS, CG
                      #                                   parallel = 8))

@@

```{r}
estimate_relation(m_e) |> 
  ggplot(aes(x=Gender, y=Predicted)) +
  geom_pointrange(aes(ymin=CI_low, ymax=CI_high, color = Gender), position=position_dodge(width=0.5)) +
 scale_color_manual(values=c("Male"="#E91E63", "Female"="#FF9800"), guide="none") +  labs(y="Arousal") +
  theme_abyss()
```

@@

```{r}
valence <- df |> 
  ggplot(aes(x=Valence)) +
  geom_bar(fill="#03A9F4") +
  scale_y_sqrt(expand = c(0, 0)) +
  labs(title = "Valence", ) +
  theme_abyss() +
  theme(plot.title = element_text(hjust = 0.5, face="bold"))

@@

df |> 
  mutate(ConditionBelief = as.factor(ConditionBelief)) |> 
  mutate(ConditionBelief = case_when(
    ConditionBelief == "False" ~ "Not Believed",
    ConditionBelief == "True" ~ "Believed",)) |>
  ggplot(aes(x=Valence, fill=Gender)) +
  geom_bar(position = "identity", binwidth = 0.5) +
  facet_grid(Gender~ConditionBelief, scales="free_y") +
  scale_color_manual(values=c("red", "white"), guide="none") +
  scale_fill_manual(values=c("Female"="#E91E63", "Male"="#FF9800"), guide="none") +
  # scale_y_sqrt(expand = c(0, 0)) +
  labs(title = "Valence to images believed or not to be AI-Gnerated") +
  theme_abyss() +
  theme(plot.title = element_text(hjust = 0.5, face="bold"))
```

@@

The analysis revealed that on average **women rate erotic stimuli significantly lower in valence than men**.

```{r}
m_v <- glmmTMB::glmmTMB(Valence ~ Gender + (1|Participant), family=glmmTMB::ordbeta(),
                      data=df,
                      control = glmmTMB::glmmTMBControl(parallel = 8))
                      # control = glmmTMB::glmmTMBControl(optimizer=stats::optim, # nlminb, optim
                      #                                   optArgs = list(method = "BFGS"),  #Nelder-Mead, BFGS, CG
                      #                                   parallel = 8))

@@

m_arousal <- glmmTMB::glmmTMB(Arousal ~ Gender/ Condition + 
                                (1| Participant) + (1|Stimulus), family=glmmTMB::ordbeta(),
                              data=df, control = glmmTMB::glmmTMBControl(parallel = 8))

@@

# marginaleffects::avg_slopes(m_arousal, variables="Condition", by="Gender") |>
#   results_table()

@@

### Moderators

This model explores whether various factors such as **attitudes towards AI, knowledge about AI, frequency of porn consumption, and sexual activity** moderate the relationship between gender, image relevance (specifically AI-generated versus photographs), and arousal ratings.

```{r}
test_moderator <- function(df, outcome="Arousal", moderator="Bait_Visual") {
  f <- paste0(outcome, " ~ Gender / (Condition * ", moderator, ") + (Condition | Participant) + (1|Stimulus)")
  r <- glmmTMB::glmmTMB(as.formula(f),
                      data = df,
                      family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8)) |>
    parameters::parameters() |> 
    as.data.frame() |> 
    select(-df_error, -Effects, -Group, -Component, -SE)
  r$Moderator <- moderator
  r$Outcome <- outcome
  insight::format_table(r[c(7, 8), ])
}

moderator_results <- data.frame()
for(m in c("BAIT_VideosRealistic", "BAIT_TextRealistic", "BAIT_ExpertAI", "PornFrequency", "SexualActivity")) {
  moderator_results <- rbind(moderator_results,
                             test_moderator(df, "Arousal", m))
}

display(moderator_results)
```

```{r}
feedback_results <- data.frame()
for(m in c("Feedback_NoFacesAttractive", "Feedback_SomeFacesAttractive", "Feedback_AIMoreAttractive", 
           "Feedback_AILessAttractive", "Feedback_DiffObvious", "Feedback_DiffSubtle", "Feedback_DiffNone" ,
           "Feedback_LabelsIncorrect", "Feedback_LabelsReversed", "Feedback_AllReal", "Feedback_AllFake",
           "Feedback_AllRealConfidence", "Feedback_AllFakeConfidence" ,  "Feedback_Enjoyment")){ 
  feedback_results <- rbind(feedback_results,
                            test_moderator(df, "Arousal", m))
}
display(feedback_results)
```
